---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# promptr

<!-- badges: start -->
<!-- badges: end -->

The goal of `promptr` is to create a straightforward interface for `R` users to format and submit prompts to OpenAI's Large Language Models (LLMs).

## Installation

You can install the development version of `promptr` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("joeornstein/promptr")
```

## Example

The package workflow is built around two functions: `format_prompt()` and `complete_prompt()`. The first allows you to format a prompt from three inputs.

```{r}
library(promptr)

prompt <- format_prompt(text = 'I feel positively morose.', 
                        instructions = 'Classify the following text as sad or happy.')
prompt
```

This is a **zero-shot** prompt (no labeled examples provided).

Once you've formatted the prompt, you can submit it to an LLM through the OpenAI API using the `complete_prompt()` function. 

```{r}
complete_prompt(prompt)
```

Pretty good, but these models often perform better if we provide few-shot examples.

```{r}
examples <- data.frame(
  text = c('What a pleasant day!', 
           'Oh bother.',
           'Merry Christmas!',
           ':-('),
  label = c('happy', 'sad', 'happy', 'sad')
)

prompt <- format_prompt(
  text = 'I feel positively morose.', 
  instructions = 'Classify the following text as sad or happy.',
  examples = examples
  )

prompt

complete_prompt(prompt)
```

The complete pipeline:

```{r}
'What a joyous day...for our adversaries.' |> 
  format_prompt(instructions = 'Classify this text as happy or sad.',
                examples = examples) |> 
  complete_prompt()
```

